%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Awesome Cover Letter
% XeLaTeX Template
% Version 1.1 (9/1/2016)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original authors:
% Claud D. Park (posquit0.bj@gmail.com)
% Lars Richter (mail@ayeks.de)
% With modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template must be compiled with XeLaTeX, the below lines will ensure this
%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt, a4paper]{awesome-cv} % A4 paper size by default, use 'letterpaper' for US letter

\geometry{left=2cm, top=1.5cm, right=2cm, bottom=2cm, footskip=.5cm} % Configure page margins with geometry
 
\fontdir[fonts/] % Specify the location of the included fonts

% Color for highlights
\colorlet{awesome}{awesome-red} % Default colors include: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange, awesome-nephritis, awesome-concrete, awesome-darknight
%\definecolor{awesome}{HTML}{CA63A8} % Uncomment if you would like to specify your own color

% Colors for text - uncomment and modify
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad} % If you would like to change the social information separator from a pipe (|) to something else

%----------------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%----------------------------------------------------------------------------------------

\name{Statement of Purpose:}{UCSB}
\address{CHANG LIU\\Department of Astronomy, Peking University}

\email{ptg.cliu@pku.edu.cn}
\homepage{https://slowdiveptg.github.io}
\github{slowdivePTG}
%\skype{skypeid}
%\stackoverflow{SOid}{SOname}
%\twitter{@twit}
%\linkedin{linkedin name}
%\reddit{reddit account}
%\xing{xing name}
%\ORCID{https://orcid.org/0000-0002-7866-4531} % Other text you want to include on this line

%\position{Undergraduate Student in Astrophysics} % Your expertise/fields
%\quote{``Explore the universe, benefit the society."} % A quote or statement

\makecvfooter{\today}{Chang Liu~~~·~~~State of Purpose}{\thepage} % Specify the letter footer with 3 arguments: (<left>, <center>, <right>), leave any of these blank if they are not needed
%----------------------------------------------------------------------------------------
%	RECIPIENT/POSITION/LETTER INFORMATION
%	All of the below lines must be filled out
%----------------------------------------------------------------------------------------

\recipient{Graduate Student}{Caltech\\1200 E California Boulevard\\Pasadena, CA 91125} % The company being applied to

\letterdate{\today} % The date on the letter, default is the date of compilation

\lettertitle{Statement of Purpose} % The title of the letter

\letteropening{Dear Mr./Ms./Dr. LastName,} % How the letter is opened

\letterclosing{Sincerely,} % How the letter is closed

\letterenclosure[Attached]{Curriculum Vitae} % Any enclosures with the letter

\makecvfooter{\today}{Chang Liu~~~·~~~Statement of Purpose: UCSB}{} % Specify the letter footer with 3 arguments: (<left>, <center>, <right>), leave any of these blank if they are not needed
  
%----------------------------------------------------------------------------------------

\begin{document}

\makecvheader % Print the header

%\makelettertitle % Print the title

%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------

\begin{cvletter}

%------------------------------------------------

\input{SoP}

\lettersection{Why UCSB? - Academic Interests}
UCSB is one of the world’s leaders in astronomy. In the Kavli Institute for Theoretical Physics (KITP), theorists and observers from all over the world congregate and work together to unlock the potential of state-of-the-art astronomical instruments or exploit a synergy of various subfields, for a flexible range of time. These programs are also open to doctoral students. For graduate students at UCSB, independent research is highly emphasized. Students would have access to diverse knowledge via courses in both physics and astronomy as well as seminars and conferences. With access to Physics Computing Services at UCSB, students can also enjoy the high performance calculation in modeling all kinds of astrophysical environments. As a member of a spontaneously organized journal club of astrophysics within us undergraduate students, I deeply understand that meeting regularly with students in other subfields of physics will broaden my pursuit in astrophysics and hone my academic presentation skills. 

I am not too surprised to find that UCSB meets so perfectly with my research experience and interests. \textbf{Prof. Lars Bildsten} has been interested in theoretical puzzles of transient for decades and has been working recently in understanding the fates of massive stars using simulation with stellar evolution code like \texttt{MESA}, to which my ambition of better understanding the nature of supernovae with detailed 3-d simulations is closely related. \textbf{Prof. Andy Howell} is the leader of the supernova group at Las Cumbres Observatory Global Telescope Network (LCOGT) exploring the transient sky. I do admire his observational work in searching for luminous supernovae and constraining cosmological parameters, for which my experience in time-domain astronomy and data analysis would be of use. Besides, with high enthusiasm and plenty of experience in hydrodynamical simulations, and after attending \textbf{Prof. Peng Oh}’s talk at UC Santa Cruz on the exciting work of cold gas in galactic halos on Oct 23, I am also attracted by MHD simulations in understanding the gas behavior in the galactic scale.

I do appreciate it if you could consider my application. I am looking forward to meeting with you for a more detailed talk soon.
%------------------------------------------------

\end{cvletter}

%----------------------------------------------------------------------------------------

%\makeletterclosing % Print the signature and enclosures

\end{document}