%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Awesome Cover Letter
% XeLaTeX Template
% Version 1.1 (9/1/2016)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original authors:
% Claud D. Park (posquit0.bj@gmail.com)
% Lars Richter (mail@ayeks.de)
% With modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template must be compiled with XeLaTeX, the below lines will ensure this
%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt, a4paper]{awesome-cv} % A4 paper size by default, use 'letterpaper' for US letter

\geometry{left=2.54cm, top=1.5cm, right=2.54cm, bottom=2cm, footskip=.5cm} % Configure page margins with geometry
 
\fontdir[fonts/] % Specify the location of the included fonts

% Color for highlights
\colorlet{awesome}{awesome-red} % Default colors include: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange, awesome-nephritis, awesome-concrete, awesome-darknight
%\definecolor{awesome}{HTML}{CA63A8} % Uncomment if you would like to specify your own color

% Colors for text - uncomment and modify
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad} % If you would like to change the social information separator from a pipe (|) to something else

%----------------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%----------------------------------------------------------------------------------------

\name{Academic Statement of}{Purpose}
\position{Astronomy \& Astrophysics Ph.D.} 
\address{CHANG LIU\\U-M ID: 70531600}

\email{ptg.cliu@pku.edu.cn}
\homepage{https://slowdiveptg.github.io}
\github{slowdivePTG}
%\skype{skypeid}
%\stackoverflow{SOid}{SOname}
%\twitter{@twit}
%\linkedin{linkedin name}
%\reddit{reddit account}
%\xing{xing name}
%\ORCID{https://orcid.org/0000-0002-7866-4531} % Other text you want to include on this line

%\position{Undergraduate Student in Astrophysics} % Your expertise/fields
%\quote{``Explore the universe, benefit the society."} % A quote or statement

\makecvfooter{\today}{Chang Liu~~~·~~~State of Purpose}{\thepage} % Specify the letter footer with 3 arguments: (<left>, <center>, <right>), leave any of these blank if they are not needed
%----------------------------------------------------------------------------------------
%	RECIPIENT/POSITION/LETTER INFORMATION
%	All of the below lines must be filled out
%----------------------------------------------------------------------------------------

\recipient{Company Recruitment Team}{Initech Inc.\\4120 Freidrich Ln.\\Austin, TX 78744} % The company being applied to

\letterdate{\today} % The date on the letter, default is the date of compilation

\lettertitle{Job Application for Middle Manager} % The title of the letter

\letteropening{Dear Mr./Ms./Dr. LastName,} % How the letter is opened

\letterclosing{Sincerely,} % How the letter is closed

\letterenclosure[Attached]{Curriculum Vitae} % Any enclosures with the letter

\makecvfooter{\today}{Chang Liu~~~·~~~Statement of Purpose: University of Michigan}{} % Specify the letter footer with 3 arguments: (<left>, <center>, <right>), leave any of these blank if they are not needed
  
%----------------------------------------------------------------------------------------

\begin{document}

\makecvheader % Print the header

%\makelettertitle % Print the title

%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------

\begin{cvletter}

%------------------------------------------------

\input{SoP}

\lettersection{Why U-M? - Academic Interests}

University of Michigan has been one of the leaders in astronomy since its foundation. Faculty at U-M work on a broad field of astrophysics and combine the latest observations with rapidly growing computational methods to answer the key questions in different areas. The group of extreme astrophysics makes use of world-class ground- \& space-based telescopes including Magellan, Chandra, and Swift, while the star \& planetary group is highly evolved in ALMA. Students at U-M are fortunate enough to be able to receive training as observers in MDM and Angell Hall Observatory. For graduate students at U-M, research are highly emphasized. Students are encouraged to work under the supervision of various faculty members before focusing on the thesis, which would enable me to explore the breadth of observational and computational astrophysics. Frequent oral presentations and academic writing training will definitely hone my skills as a rising astrophysicist.

I am not too surprised to find that University of Michigan meets so perfectly with my research experience. \textbf{Prof. Edwin Bergin} works on astrochemistry to understand planet formation and origin of biogenetic species with both data from ALMA and chemical simulations. My former simulation work on the genesis of prebiotic species in the Milky Way is closely related to his interests, and inspires me to go further in revealing the physical processes in protoplanetary disks under irradiation. I am also interested in \textbf{Prof. Emily Rauscher}’s 3-D simulations on exoplanets to find out how atmospheric circulation patterns on hot Jupiters are influenced by magnetic field and radiation. Besides, as I am also attracted by the nature of high energy transients, I do admire \textbf{Prof. Kayhan Gultekin}’s contribution on black holes and accretion processes, especially on determining the mass of black holes with observable properties of the accretion disk. \textbf{Prof. Jon Miller}’s work on probing the spins of black holes with X-ray properties is also what I would like to explore. My experiences on both observational and computational study on compact objects allow me to dive into the study on hydrodynamics and radiation around black holes.

I do appreciate it if you could consider my application. I am looking forward to meeting with you for a more detailed talk soon.
%------------------------------------------------

\end{cvletter}

%----------------------------------------------------------------------------------------

%\makeletterclosing % Print the signature and enclosures

\end{document}